---
title: "boing"
author: "MD"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(readxl)
library(car)
library(phyloseq)
library(emmeans)
library(vegan)
library(ggbeeswarm)
library(pairwiseAdonis)
library(patchwork)
```


```{r}

P.count <- readRDS('phyloseq/P.count.cycle.RDS')%>% 
  subset_samples(., Reads_16S > 10000) %>% 
  subset_samples(., Sample_Type == 'Rhizosphere soil')
kegg <- read_excel('EMU_database.GIBBs.KO.PICRUST2.xlsx', sheet='EMU_database.GIBBs.PICRUSt2', range='B9:BE17565')
kegg <- kegg %>%
  mutate_if(is.numeric, replace_na, replace=0)
```


```{r}
colnames(tax_table(P.count)) <- c('Kingdom', 'Phylum', 'Class', 'Order', 'Family', 'Genus', 'Species')
p.fs <- subset_samples(P.count, Autoclave_status == 'Sterile Soil' 
                            & Fert_Pattern != "Unfertilized-Unfertilized"
                            & Fert_Pattern != "Unfertilized-Fertilized")
p.us <- subset_samples(P.count, Autoclave_status == 'Sterile Soil' 
                            & Fert_Pattern != "Fertilized-Unfertilized"
                            & Fert_Pattern != "Fertilized-Fertilized")
p.fn <- subset_samples(P.count, Autoclave_status == 'Not Sterile Soil' 
                            & Fert_Pattern != "Unfertilized-Unfertilized"
                            & Fert_Pattern != "Unfertilized-Fertilized")
p.un <- subset_samples(P.count, Autoclave_status == 'Not Sterile Soil' 
                            & Fert_Pattern != "Fertilized-Unfertilized"
                            & Fert_Pattern != "Fertilized-Fertilized")

```

# Fertilized sterile

## Generate df for each dom group

### Modern - wild
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fs, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','Wild'))
mod_wild<-data.frame(microbiomeMarker::marker_table(out.glom)) %>% 
  mutate(., Group = 'Modern-Wild')
```

### Modern - no plant
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fs, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','No-plant'))
mod_noplant<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'Modern-No.Plant')
```


### No plant - wild

```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fs, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Wild','No-plant'))
noplant_wild<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'No.Plant-Wild')
```

## Finalize and clean combined df
### Combine df
```{r}
all <- rbind(mod_noplant, mod_wild, noplant_wild)
```

### Add significance
```{r}
all$sig <- ifelse(all$padj>0.05, "NS",
                                       ifelse(all$padj==0.05, "NS",
                                              ifelse(abs(all$ef_logFC)<2, "NS", "sig")))
all$sig.trt <- paste(all$enrich_group,all$sig)


all$colors <- ifelse(all$sig=="NS", "NS",
                        ifelse(all$sig.trt=='Modern sig',"Modern",
                               ifelse(all$sig.trt=='No.plant sig','No Plant',
                                      ifelse(all$sig.trt== "Wild sig", "Wild", NA))))

all <- all %>%
mutate(colors = as_factor(colors)) %>%
mutate(colors = fct_relevel(colors, "No Plant", "Wild", "Modern", "NS"))
all <- all %>%
mutate(Group = as_factor(Group)) %>%
mutate(Group = fct_relevel(Group, "No.Plant-Wild", "Modern-Wild", "Modern-No.Plant"))
all<- arrange(all, -log(padj),ef_logFC)

```

## graph
### Volcano plot

```{r}
p.fsvol<-ggplot(data=all)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  scale_fill_manual(values = c('yellow3','darkorange2','darkblue','gray70'))+
  theme_classic()+
  facet_wrap(~Group, ncol=1, scales = "free")+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        legend.title = element_blank());p.fsvol
```

### dot plot


```{r}
d <- filter(all, padj < 0.05 & abs(ef_logFC)>2)
d.list <- d$feature 
keggsub <- filter(kegg, Species %in% d.list)
names(d)[names(d) == 'feature'] <- 'Species'
d.kegg <- left_join(d,keggsub, by = 'Species') %>% 
  filter(!NSTI=='NA')

d<- pivot_longer(d.kegg, cols=hcnA:nosZ, names_to = 'Gene', values_to = 'value') %>%   filter(!value==0)

d$Function <- ifelse(d$Gene=="hcnA", "Biocontrol",
                     ifelse(d$Gene=="budA","Biocontrol",
                     ifelse(d$Gene=="budC","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.6","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.14","Biocontrol",
                     ifelse(d$Gene=="phlD","Biocontrol",
                     ifelse(d$Gene=="ituA","Biocontrol", 
                     ifelse(d$Gene=="fenA", "Biocontrol",
                     ifelse(d$Gene=="srfAA","Biocontrol",
                     ifelse(d$Gene=="rifM","Biocontrol",
                     ifelse(d$Gene=="phzE","Biocontrol",
                     ifelse(d$Gene=="ipdC","Stress",
                     ifelse(d$Gene=="acdS","Stress",
                     ifelse(d$Gene=="mbtI","Siderophore",
                     ifelse(d$Gene=="entA", "Siderophore",
                     ifelse(d$Gene=="pchB","Siderophore",
                     ifelse(d$Gene=="bglX","C decomposition",
                     ifelse(d$Gene=="bglB","C decomposition",
                     ifelse(d$Gene=="E3.2.1.21","C decomposition",  
                     ifelse(d$Gene=="amiE","N decomposition",  
                     ifelse(d$Gene=="ureC","N decomposition",  
                     ifelse(d$Gene=="pqqC", "PO4 solubility",
                     ifelse(d$Gene=="phoA","P decomposition",
                     ifelse(d$Gene=="phoD","P decomposition",
                     ifelse(d$Gene=="PHO","P decomposition",
                     ifelse(d$Gene=="appA","P decomposition", 
                     ifelse(d$Gene=="phoN","P decomposition",
                     ifelse(d$Gene=="aslA","S decomposition",
                     ifelse(d$Gene=="nifH", "N-fixation",
                     ifelse(d$Gene=="nifD","N-fixation",
                     ifelse(d$Gene=="nifK","N-fixation",
                     ifelse(d$Gene=="pmoA-amoA","Nitrification",
                     ifelse(d$Gene=="hao","Nitrification",             
                     ifelse(d$Gene=="nirB","Dissimilatory nitrate reduction",    
                     ifelse(d$Gene=="nirD","Dissimilatory nitrate reduction",              
                     ifelse(d$Gene=="nrfA", "Dissimilatory nitrate reduction",
                     ifelse(d$Gene=="nirA","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="NIT-6","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="narG","Denitrification",
                     ifelse(d$Gene=="narH","Denitrification",
                     ifelse(d$Gene=="nirK","Denitrification",    
                     ifelse(d$Gene=="nirS","Denitrification",
                     ifelse(d$Gene=="norB", "Denitrification",
                     ifelse(d$Gene=="norC","Denitrification", 
                     ifelse(d$Gene=='nosZ','Denitrification',
                     NA)))))))))))))))))))))))))))))))))))))))))))))

d<- arrange(d, Function)
d_sum <- summarise(group_by(d,Gene,Function,enrich_group,Group, Species),
                   mean.lfc = mean(ef_logFC),
                   mean.p = mean(padj))

d_sum <- filter(d_sum, Function != 'Assimilatory nitrate reduction') %>% 
         filter(., Function !=  'Dissimilatory nitrate reduction') %>% 
         filter(., Function != 'Denitrification')

d_sum <- d_sum %>%
mutate(Function = as_factor(Function)) %>%
mutate(Function = fct_relevel(Function, "Biocontrol",
                                           "Stress",
                                           "S decomposition",
                                           "C decomposition",
                                           "N decomposition",
                              "N-fixation",
                                           "Nitrification",
                                           "Siderophore",
                                           "P decomposition",
                                           "PO4 solubility"))
table(d_sum$Function)


p.bee<-ggplot(d_sum, aes(x=interaction(Species, enrich_group), y=Function, color=Gene)) + 
 geom_hline(yintercept = 1.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 2.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 3.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 4.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 5.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 6.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 7.5, color = "gray90", linewidth = 0.25)+
 geom_hline(yintercept = 8.5, color = "gray90", linewidth = 0.25)+
 geom_vline(xintercept = 0.4, color = "black", linewidth = 0.9)+
 geom_beeswarm(size = 6, cex=2, alpha=0.7) + 
 scale_color_manual(values = c("#EA4691", #acds,
                               "#6BFF33", # amie
                               "#2929F0",  # appa
                               "#BFE75D", #asla,
                               "#F9FF76", #bglb
                               "#A3A92D",  # bglx
                               "#7667A0", #buda,
                               "#3F2B78" ,#budc
                               "#26194C",  #, e32114
                               "#610185", # enta,
                               "#A0008D", # hao
                               "#A774B8", # pchb
                               "#3AF6FC",# pho,
                               "#239A9E", #phoa,
                               "#156062",  #phod
                               "#40008C",#phze, 
                               "#38A2B9", #, pqqc
                               "#38871A",#urec
                               "#E75DD6" #pmoaamoa
                               ))+
    facet_grid(~Group, scales = 'free',space = "free_x")+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90, color = 'black',hjust=0.95, vjust=0.2),
        axis.text.y = element_text(color = 'black'),
        axis.line = element_line(colour = "black"),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        axis.title.x = element_blank());p.bee
```

### Combine graphs
```{r}
p.vol/p.bee 
```


# Unfertilized sterile 

## Generate df for each dom group

### Modern - wild
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.us, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','Wild'))
mod_wild<-data.frame(microbiomeMarker::marker_table(out.glom)) %>% 
  mutate(., Group = 'Modern-Wild')
```

### Modern - no plant
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.us, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','No-plant'))
mod_noplant<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'Modern-No.Plant')
```


### No plant - wild

```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.us, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Wild','No-plant'))
noplant_wild<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'No.Plant-Wild')
```

## Finalize and clean combined df
### Combine df
```{r}
all <- rbind(mod_noplant, mod_wild, noplant_wild)
```

### Add significance
```{r}
all$sig <- ifelse(all$padj>0.05, "NS",
                                       ifelse(all$padj==0.05, "NS",
                                              ifelse(abs(all$ef_logFC)<2, "NS", "sig")))
all$sig.trt <- paste(all$enrich_group,all$sig)


all$colors <- ifelse(all$sig=="NS", "NS",
                        ifelse(all$sig.trt=='Modern sig',"Modern",
                               ifelse(all$sig.trt=='No.plant sig','No Plant',
                                      ifelse(all$sig.trt== "Wild sig", "Wild", NA))))

all <- all %>%
mutate(colors = as_factor(colors)) %>%
mutate(colors = fct_relevel(colors, "No Plant", "Wild", "Modern", "NS"))
all <- all %>%
mutate(Group = as_factor(Group)) %>%
mutate(Group = fct_relevel(Group, "No.Plant-Wild", "Modern-Wild", "Modern-No.Plant"))
all<- arrange(all, -log(padj),ef_logFC)

```

## graph
### Volcano plot

```{r}
p.usvol<-ggplot(data=all)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  scale_fill_manual(values = c('yellow3','darkblue','gray70'))+
  theme_classic()+
  ggtitle(label = "Unfertilized, Sterile")+
  facet_wrap(~Group, ncol=1, scales = "free")+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        legend.title = element_blank());p.usvol
```


# Fertilized Unsterile 
## Generate df for each dom group

### Modern - wild
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fn, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','Wild'))
mod_wild<-data.frame(microbiomeMarker::marker_table(out.glom)) %>% 
  mutate(., Group = 'Modern-Wild')
```

### Modern - no plant
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fn, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','No-plant'))
mod_noplant<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'Modern-No.Plant')
```


### No plant - wild

```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.fn, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Wild','No-plant'))
noplant_wild<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'No.Plant-Wild')
```

## Finalize and clean combined df
### Combine df
```{r}
all <- rbind(mod_noplant, mod_wild, noplant_wild)
```

### Add significance
```{r}
all$sig <- ifelse(all$padj>0.05, "NS",
                                       ifelse(all$padj==0.05, "NS",
                                              ifelse(abs(all$ef_logFC)<2, "NS", "sig")))
all$sig.trt <- paste(all$enrich_group,all$sig)


all$colors <- ifelse(all$sig=="NS", "NS",
                        ifelse(all$sig.trt=='Modern sig',"Modern",
                               ifelse(all$sig.trt=='No.plant sig','No Plant',
                                      ifelse(all$sig.trt== "Wild sig", "Wild", NA))))

all <- all %>%
mutate(colors = as_factor(colors)) %>%
mutate(colors = fct_relevel(colors, "No Plant", "Wild", "Modern", "NS"))
all <- all %>%
mutate(Group = as_factor(Group)) %>%
mutate(Group = fct_relevel(Group, "No.Plant-Wild", "Modern-Wild", "Modern-No.Plant"))
all<- arrange(all, -log(padj),ef_logFC)

```

## graph
### Volcano plot

```{r}
p.fnvol<-ggplot(data=all)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  scale_fill_manual(values = c('yellow3','darkorange2','darkblue','gray70'))+
  theme_classic()+
  ggtitle(label = "Fertilized, Not Sterile")+
  facet_wrap(~Group, ncol=1, scales = "free")+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        legend.title = element_blank());p.fnvol
```

# Unfertilized not sterile
## Generate df for each dom group

### Modern - wild
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.un, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','Wild'))
mod_wild<-data.frame(microbiomeMarker::marker_table(out.glom)) %>% 
  mutate(., Group = 'Modern-Wild')
```

### Modern - no plant
```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.un, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Modern','No-plant'))
mod_noplant<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'Modern-No.Plant')
```


### No plant - wild

```{r}
out.glom <- microbiomeMarker::run_deseq2(
  p.un, 
  group="C1_plant_condition",
  taxa_rank="Species",
  norm="RLE",
  transform="identity",
  p_adjust='fdr', 
  pvalue_cutoff=1,
  contrast=c('Wild','No-plant'))
noplant_wild<-data.frame(microbiomeMarker::marker_table(out.glom))  %>% 
  mutate(., Group = 'No.Plant-Wild')
```

## Finalize and clean combined df
### Combine df
```{r}
all <- rbind(mod_noplant, mod_wild, noplant_wild)
```

### Add significance
```{r}
all$sig <- ifelse(all$padj>0.05, "NS",
                                       ifelse(all$padj==0.05, "NS",
                                              ifelse(abs(all$ef_logFC)<2, "NS", "sig")))
all$sig.trt <- paste(all$enrich_group,all$sig)


all$colors <- ifelse(all$sig=="NS", "NS",
                        ifelse(all$sig.trt=='Modern sig',"Modern",
                               ifelse(all$sig.trt=='No.plant sig','No Plant',
                                      ifelse(all$sig.trt== "Wild sig", "Wild", NA))))

all <- all %>%
mutate(colors = as_factor(colors)) %>%
mutate(colors = fct_relevel(colors, "No Plant", "Wild", "Modern", "NS"))
all <- all %>%
mutate(Group = as_factor(Group)) %>%
mutate(Group = fct_relevel(Group, "No.Plant-Wild", "Modern-Wild", "Modern-No.Plant"))
all<- arrange(all, -log(padj),ef_logFC)

```

## graph
### Volcano plot

```{r}
p.unvol<-ggplot(data=all)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  scale_fill_manual(values = c('yellow3','darkblue','gray70'))+
  theme_classic()+
  facet_wrap(~Group, ncol=1, scales = "free")+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  ggtitle(label = "Unfertilized, Not Sterile")+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        legend.title = element_blank());p.unvol
```

### Combine graphs
```{r}
p.usvol + p.fnvol + p.unvol + plot_layout(guides = "collect") + plot_layout(axis_titles = "collect")
```


```{r}

mod_wild$sig <- ifelse(mod_wild$padj>0.05, "NS",
                                       ifelse(mod_wild$padj==0.05, "NS",
                                              ifelse(abs(mod_wild$ef_logFC)<2, "NS", "sig")))
mod_wild$sig.trt <- paste(mod_wild$enrich_group,mod_wild$sig)


mod_wild$colors <- ifelse(mod_wild$sig=="NS", "NS",
                        ifelse(mod_wild$sig.trt=='Modern sig',"Modern",
                               ifelse(mod_wild$sig.trt=='Wild sig','Wild',NA)))
mod_wild<- arrange(mod_wild, -log(padj))


p<-ggplot(data=mod_wild)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  coord_cartesian(xlim = c(-20,23))+
  scale_fill_manual(values = c('cornflowerblue','gray50','darkorange'))+
  theme_classic()+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank());p
```

```{r}

noplant_wild$sig <- ifelse(noplant_wild$padj>0.05, "NS",
                                       ifelse(noplant_wild$padj==0.05, "NS",
                                              ifelse(abs(noplant_wild$ef_logFC) <2, "NS", "sig")))
noplant_wild$sig.trt <- paste(noplant_wild$enrich_group,noplant_wild$sig)


noplant_wild$colors <- ifelse(noplant_wild$sig=="NS", "NS",
                        ifelse(noplant_wild$sig.trt=='No.plant sig',"No plant",
                               ifelse(noplant_wild$sig.trt=='Wild sig','Wild',NA)))
noplant_wild<- arrange(noplant_wild, -log(padj))

p<-ggplot(data=noplant_wild)+
  geom_point(alpha=0.85,mapping= aes(
    fill=colors, x=ef_logFC,y=-log(padj)),
    size=5,color='black',pch=21) +
  scale_fill_manual(values = c('gray50','darkorange'))+
  theme_classic()+
  labs(y=expression("-log"["10"] ~ "p" ["adj"]), 
       x=expression("log"["2"]~"Fold Change"))+
  theme(axis.text=element_text(size=10, colour = "black"), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank());p
```



```{r}
d <- filter(mod_wild, padj < 0.05)
d.list <- d$feature 
keggsub <- filter(kegg, Species %in% d.list)
names(d)[names(d) == 'feature'] <- 'Species'
d.kegg <- left_join(d,keggsub, by = 'Species') %>% 
  filter(!NSTI=='NA')

d<- pivot_longer(d.kegg, cols=hcnA:nosZ, names_to = 'Gene', values_to = 'value') %>%   filter(!value==0)

d$Function <- ifelse(d$Gene=="hcnA", "Biocontrol",
                     ifelse(d$Gene=="budA","Biocontrol",
                     ifelse(d$Gene=="budC","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.6","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.14","Biocontrol",
                     ifelse(d$Gene=="phlD","Biocontrol",
                     ifelse(d$Gene=="ituA","Biocontrol", 
                     ifelse(d$Gene=="fenA", "Biocontrol",
                     ifelse(d$Gene=="srfAA","Biocontrol",
                     ifelse(d$Gene=="rifM","Biocontrol",
                     ifelse(d$Gene=="phzE","Biocontrol",
                     ifelse(d$Gene=="ipdC","Stress",
                     ifelse(d$Gene=="acdS","Stress",
                     ifelse(d$Gene=="mbtI","Siderophore",
                     ifelse(d$Gene=="entA", "Siderophore",
                     ifelse(d$Gene=="pchB","Siderophore",
                     ifelse(d$Gene=="bglX","C decomposition",
                     ifelse(d$Gene=="bglB","C decomposition",
                     ifelse(d$Gene=="E3.2.1.21","C decomposition",  
                     ifelse(d$Gene=="amiE","N decomposition",  
                     ifelse(d$Gene=="ureC","N decomposition",  
                     ifelse(d$Gene=="pqqC", "PO4 solubility",
                     ifelse(d$Gene=="phoA","P decomposition",
                     ifelse(d$Gene=="phoD","P decomposition",
                     ifelse(d$Gene=="PHO","P decomposition",
                     ifelse(d$Gene=="appA","P decomposition", 
                     ifelse(d$Gene=="phoN","P decomposition",
                     ifelse(d$Gene=="aslA","S decomposition",
                     ifelse(d$Gene=="nifH", "N-fixation",
                     ifelse(d$Gene=="nifD","N-fixation",
                     ifelse(d$Gene=="nifK","N-fixation",
                     ifelse(d$Gene=="pmoA-amoA","Nitrification",
                     ifelse(d$Gene=="hao","Nitrification",             
                     ifelse(d$Gene=="nirB","Dissimilatory nitrate reduction",    
                     ifelse(d$Gene=="nirD","Dissimilatory nitrate reduction",              
                     ifelse(d$Gene=="nrfA", "Dissimilatory nitrate reduction",
                     ifelse(d$Gene=="nirA","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="NIT-6","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="narG","Denitrification",
                     ifelse(d$Gene=="narH","Denitrification",
                     ifelse(d$Gene=="nirK","Denitrification",    
                     ifelse(d$Gene=="nirS","Denitrification",
                     ifelse(d$Gene=="norB", "Denitrification",
                     ifelse(d$Gene=="norC","Denitrification", 
                     ifelse(d$Gene=='nosZ','Denitrification',
                     NA)))))))))))))))))))))))))))))))))))))))))))))

d<-d %>% dplyr::select(Species, enrich_group, Fert_Pattern*Autoclave_status*C1_plant_condition, ef_logFC, padj, Fert, Gene, Function)
d<- arrange(d, Function)
d_sum <- summarise(group_by(d,Gene,Function,enrich_group, Species),
                   mean.lfc = mean(ef_logFC),
                   mean.p = mean(padj))

d_sum <- filter(d_sum, Function != 'Assimilatory nitrate reduction') %>% 
         filter(., Function !=  'Dissimilatory nitrate reduction') %>% 
         filter(., Function != 'Denitrification')

level_order <- factor(d_sum$Function, levels=c( "Biocontrol",
                                           "Stress",
                                           "S decomposition",
                                           "C decomposition",
                                           "N decomposition",
                                           "Nitrification",
                                           "N-fixation",
                                           "Siderophore",
                                           "P decomposition",
                                           "PO4 solubility"))


p<-ggplot(d_sum, aes(x=Species, y=level_order, color=Gene)) + 
  geom_beeswarm(size = 4, cex=1, alpha =  0.7) + 
  scale_color_manual(values = c("#EA4691", "#6BFF33", '#BFE75D',
                                "#F9FF76", "#A3A92D", "#7667A0",
                                "#3F2B78", "#26194C", "#A2CACB",
                                "#662341", "#1BB74B", "#39FDA4",
                                "#145437", "#239A9E", "#156062",
                                "#A2CACB", "#38A2B9", "#38871A"))+
   facet_wrap(~enrich_group, ncol=1,scales = 'free')+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.line = element_line(colour = "black"),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_blank());p
```

```{r}
d <- filter(mod_noplant, padj < 0.05)
d.list <- d$feature 
keggsub <- filter(kegg, Species %in% d.list)
names(d)[names(d) == 'feature'] <- 'Species'
d.kegg <- left_join(d,keggsub, by = 'Species') %>% 
  filter(!NSTI=='NA')

d<- pivot_longer(d.kegg, cols=hcnA:nosZ, names_to = 'Gene', values_to = 'value') %>%   filter(!value==0)

d$Function <- ifelse(d$Gene=="hcnA", "Biocontrol",
                     ifelse(d$Gene=="budA","Biocontrol",
                     ifelse(d$Gene=="budC","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.6","Biocontrol",
                     ifelse(d$Gene=="E3.2.1.14","Biocontrol",
                     ifelse(d$Gene=="phlD","Biocontrol",
                     ifelse(d$Gene=="ituA","Biocontrol", 
                     ifelse(d$Gene=="fenA", "Biocontrol",
                     ifelse(d$Gene=="srfAA","Biocontrol",
                     ifelse(d$Gene=="rifM","Biocontrol",
                     ifelse(d$Gene=="phzE","Biocontrol",
                     ifelse(d$Gene=="ipdC","Stress",
                     ifelse(d$Gene=="acdS","Stress",
                     ifelse(d$Gene=="mbtI","Siderophore",
                     ifelse(d$Gene=="entA", "Siderophore",
                     ifelse(d$Gene=="pchB","Siderophore",
                     ifelse(d$Gene=="bglX","C decomposition",
                     ifelse(d$Gene=="bglB","C decomposition",
                     ifelse(d$Gene=="E3.2.1.21","C decomposition",  
                     ifelse(d$Gene=="amiE","N decomposition",  
                     ifelse(d$Gene=="ureC","N decomposition",  
                     ifelse(d$Gene=="pqqC", "PO4 solubility",
                     ifelse(d$Gene=="phoA","P decomposition",
                     ifelse(d$Gene=="phoD","P decomposition",
                     ifelse(d$Gene=="PHO","P decomposition",
                     ifelse(d$Gene=="appA","P decomposition", 
                     ifelse(d$Gene=="phoN","P decomposition",
                     ifelse(d$Gene=="aslA","S decomposition",
                     ifelse(d$Gene=="nifH", "N-fixation",
                     ifelse(d$Gene=="nifD","N-fixation",
                     ifelse(d$Gene=="nifK","N-fixation",
                     ifelse(d$Gene=="pmoA-amoA","Nitrification",
                     ifelse(d$Gene=="hao","Nitrification",             
                     ifelse(d$Gene=="nirB","Dissimilatory nitrate reduction",    
                     ifelse(d$Gene=="nirD","Dissimilatory nitrate reduction",              
                     ifelse(d$Gene=="nrfA", "Dissimilatory nitrate reduction",
                     ifelse(d$Gene=="nirA","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="NIT-6","Assimilatory nitrate reduction",
                     ifelse(d$Gene=="narG","Denitrification",
                     ifelse(d$Gene=="narH","Denitrification",
                     ifelse(d$Gene=="nirK","Denitrification",    
                     ifelse(d$Gene=="nirS","Denitrification",
                     ifelse(d$Gene=="norB", "Denitrification",
                     ifelse(d$Gene=="norC","Denitrification", 
                     ifelse(d$Gene=='nosZ','Denitrification',
                     NA)))))))))))))))))))))))))))))))))))))))))))))

d<-d %>% dplyr::select(Species, enrich_group, Fert_Pattern*Autoclave_status*C1_plant_condition, ef_logFC, padj, Fert, Gene, Function)
d<- arrange(d, Function)
d_sum <- summarise(group_by(d,Gene,Function,enrich_group, Species),
                   mean.lfc = mean(ef_logFC),
                   mean.p = mean(padj))

d_sum <- filter(d_sum, Function != 'Assimilatory nitrate reduction') %>% 
         filter(., Function !=  'Dissimilatory nitrate reduction') %>% 
         filter(., Function != 'Denitrification')

level_order <- factor(d_sum$Function, levels=c( "Biocontrol",
                                           "Stress",
                                           "S decomposition",
                                           "C decomposition",
                                           "N decomposition",
                                           "Nitrification",
                                           "N-fixation",
                                           "Siderophore",
                                           "P decomposition",
                                           "PO4 solubility"))


p<-ggplot(d_sum, aes(x=Species, y=level_order, color=Gene)) + 
  geom_beeswarm(size = 4, cex=1, alpha =  0.7) + 
  scale_color_manual(values = c("#EA4691", "#6BFF33", '#BFE75D',
                                "#F9FF76", "#A3A92D", "#7667A0",
                                "#3F2B78", "#26194C", "#A2CACB",
                                "#662341", "#1BB74B", "#39FDA4",
                                "#145437", "#239A9E", "#156062",
                                "#A2CACB", "#38A2B9", "#38871A"))+
   facet_wrap(~enrich_group, ncol=1,scales = 'free')+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90, color = 'black'),
        axis.text.y = element_text(color = 'black'),
        axis.line = element_line(colour = "black"),
        axis.title.y = element_blank(),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_blank());p
```




```{r}
d <- data.frame(sample_data(P.rel))

data <- data.frame(t(otu_table(P.rel)))
data <- decostand(data, method='hellinger')

dist <- vegdist(data, method='bray')

ord <- capscale(dist ~ Fert_Pattern*Autoclave_status*C1_plant_condition, data=d)
adonis2(dist ~  Fert_Pattern*Autoclave_status*C1_plant_condition, data=d, perm=999)

pairwise.adonis(dist,factors=d$Fert_Pattern, p.adjust.m = "fdr")
pairwise.adonis(dist,factors=d$Autoclave_status, p.adjust.m = "fdr")
pairwise.adonis(dist,factors=d$C1_plant_condition, p.adjust.m = "fdr")

```

```{r}

ev <- eigenvals(ord)
Axis1_exp = round(ev[1] / sum(ev) * 100, 1)
Axis2_exp = round(ev[2] / sum(ev) * 100, 1)

axes <- as.data.frame(vegan::scores(ord, display="sites", choices=c(1:2)))
names(axes) <- c("Axis1", "Axis2")
axes <- cbind(d, axes)

p<-ggplot(data=axes, aes(x=Axis1, y=Axis2, fill=C1_plant_condition, shape=Fert_Pattern)) +
  geom_point(size=6,color='black') +
  stat_ellipse(aes(group= Autoclave_status, color= Autoclave_status), type='t', level=0.95) +
scale_color_brewer(palette = 'Paired')+
  scale_fill_brewer(palette = 'Paired')+
    # scale_fill_manual(values = rev(brewer.pal(8, "Paired")))+
  # scale_color_manual(values = rev(brewer.pal(8, "Paired")))+
  scale_shape_manual(values=c(21,22,23,24)) +
  guides(fill = guide_legend(
    override.aes=list(shape = rep(21)))) +
  labs(x=paste0('CAP1 (', Axis1_exp, '%)'), 
       y=paste0('CAP2 (', Axis2_exp, '%)'),
       alpha='none') +
  theme_classic();p
```

